A Study on Common Bug Fix Patterns in Rust

### 2022-10-29 related.tex
flattened everything ;((

We would characterize our work as the Rust version of what was done in~\cite{hanam2016discovering} and~\cite{yang2022mining}. Like~\cite{hanam2016discovering}, we used DBSCAN to cluster fixes. However, our novel program encoding approach differs from what they did. In~\cite{hanam2016discovering}, they introduced Feature Properties table, which is a categorization for program elements. Encoding programs based on this table resulted in a order-sensitive encoding, however, it made the datapoints sparse. Moreover, like~\cite{yang2022mining}, we introduced patterns in two different categories. In our case there were general and language-specific patterns; for Rust, the language-specific patterns were related to the borrow checker (BC patterns). However, in oppose to our paper, in~\cite{yang2022mining}, they did a much more elaborate manual analysis, as in their data collection, they only collected general information about the single hunk changes (e.g. the number of variables, or arguments).

>>>>

We would characterize our work as the Rust version of what was done in~\cite{hanam2016discovering} and~\cite{yang2022mining}. Like~\cite{hanam2016discovering}, we used DBSCAN to cluster fixes. However, our novel program embedding approach differs from what they did. In~\cite{hanam2016discovering}, they introduced Feature Properties table, which is a categorization for program elements. Embedding programs based on this table resulted in a order-sensitive embedding, however, it made the datapoints sparse. Moreover, like~\cite{yang2022mining}, we introduced patterns in two different categories. In our case there were general and language-specific patterns; for Rust, the language-specific patterns were related to the borrow checker (BC patterns). However, in oppose to our paper, in~\cite{yang2022mining}, they did a much more elaborate manual analysis, as in their data collection, they only collected general information about the single hunk changes (e.g. the number of variables, or arguments).
